ML-Runner: A Scalable Cloud Service for Machine \& Distributed Learning

### 2018-05-11 Paper.tex
fixed some issues
fixed typos

In \lfi, the set of configurations is infered from $O$ in the manner just described (\ie as the cross of the valid options for each $\param$).
\lfi subsequently creates a docker container containing the code $C$ and environment variables containing the parameter settings for each configuration.
It uploads this container to S3 under a key $K$, records loggin information for this $P$, $C$, $O$, and $U$ in a DynamoDB table.
Finally \lfi pushes a message $M$ = ($P$, $K$, `New Version') to SQS containing the location of the container in S3 and the project id for the experiment.

@@

\subsection{Implementation Details} \label{ch:implementation}

\end{multicols}
\subsubsection{Frontend}
We implemented a React front end which we deployed on an Nginx server on an AWS EC2 instance.
Our front end made use of a number of frameworks including:

@@

We provided pages for logging in, registering, learning about the service, checking one's profile, viewing a dashboard, creating new experiments, and viewing and running experiments.

@@

% -------------- TERMINOLOGY --------------
% -----------------------------------------
\section{Terminology} \label{ch:Terminology}

\begin{description}
\item[address] triple abc
\end{description}

>>>>

In \lfi, the set of configurations is infered from $O$ in the manner just described (\ie as the cross of the valid options for each $\param$).
\lfi subsequently creates a docker container containing the code $C$ and environment variables containing the parameter settings for each configuration.
It uploads this container to S3 under a key $K$ and records loggin information for this $P$, $C$, $O$, and $U$ in a DynamoDB table.
Finally \lfi pushes a message $M$ = ($P$, $K$, `New Version') to SQS containing the location of the container in S3 and the project id for the experiment.

@@

\end{multicols}
\subsection{Implementation Details} \label{ch:implementation}
\subsubsection{Frontend}
We implemented a React front end which we deployed on an Nginx server on an AWS EC2 instance.
Our front end made use of a number of frameworks including:

@@

We provided pages for logging in, registering, learning about the service, checking one's profile, viewing a dashboard, creating new experiments, and viewing and running experiments.
The full frontend code is available at \url{https://github.com/6998/webapp}.

@@
